\chapter{Properties of Systems (Oppenheim 1.6)}

\section{Single-Input Single-Output (SISO) Systems}

\begin{definition}
    []
    A System $$S : \mathbb{C}^{\mathbb{R}} \to \mathbb{C}^{\mathbb{R}}$$
    is said to be \textit{memoryless} if the output at time $t$ depends only on the input at time $t$. That is:
    $$ y(t) = (5(x))(t) = g(x(t))$$
    for some function $g \to \mathbb{C} \to \mathbb{C}$.\\
    \textit{I.e. the function doesn't remember previous inputs.}
\end{definition}

\begin{example}
    [Memoryless System]
    Full-wave rectifier system is memoryless.\\
    $$x(t) \to \boxed{| \cdot |} \to y(t) = |x(t)|$$
\end{example}


\begin{definition}
    [Anticipation]
    A system is said to be \textit{anticipative} if the output at time $t$ depends on future inputs. That is:
    $$ y(t) = (A(x))(t) = g(x(t+1))$$
    for some function $g \to \mathbb{C} \to \mathbb{C}$.\\
\end{definition}

\begin{definition}
    [Delay Lines]
    $$x[n] \to \boxed{\text{Delay}} \to x[n-1] \to \boxed{\text{Delay}}\to y(t) = x(t-2)$$
    There can be as many delays as you want in the line.
\end{definition}

\begin{definition}
    [Invertible System]
    A system is said to be \textit{invertible} if different inputs produce different outputs. That is, S is \textit{injective}
    \begin{align*}
        x_1(t)            & \neq x_2(t) \implies S(x_1)(t) \neq S(x_2)(t) \\
        \therefore S(x_1) & = S(x_2) \implies x_1 = x_2
    \end{align*}
\end{definition}

\begin{corollary}
    []
    If $S$ is invertible, then $\exists W$ such that
    $$S(W(x)) = \text{id} \qquad \text{identity system}$$
    $$x(t) \to \boxed{S} \to \boxed[W] \to y(t) = x(t)$$
\end{corollary}

\begin{definition}
    [Causal System]
    A system $S : \mathbb{C}^{\mathbb{R}} \to \mathbb{C}^{\mathbb{R}}$ is casuaal if the output at time $t$ depends only on the input at time $t$ and previous times. That is:
    A system
    $$        x_1(t) = x_2(t) \quad \forall t < t_0 \implies S(x_1)(t) = S(x_2)$$
    \\\textit{I.e. the system doesn't predict the future, or doesn't predict bifercation.}
\end{definition}

\begin{definition}
    [Stable System]
    A system $S : \mathbb{C}^{\mathbb{R}} \to \mathbb{C}^{\mathbb{R}}$ is stable if bounded inputs produce bounded outputs. That is:
    $$|x(t)| < B \quad \forall t \implies \exists C(B) \quad |S(x)(t)| \leq C(B) \quad \forall t$$
\end{definition}

\begin{definition}
    [Linaer System]
    A system $S : \mathbb{C}^{\mathbb{R}} \to \mathbb{C}^{\mathbb{R}}$ is said to preserve linear combinations for all signals. That is:
    $$S(a_1 x_1 + a_2 x_2) = a_1 S(x_1) + a_2 S(x_2)$$
    or equivalently
    $$S(\sum_{i=1}^{n} a_i x_i) = \sum_{i=1}^{n} a_i S(x_i)$$q
\end{definition}

\begin{theorem}
    [Linear-time iI,nvariant (LTI) System]+
    are linear and time-invariant.
\end{theorem}